Tennis

### 2019-12-18 PaperDraft.Rmd
changing positions of figures

---
title: "Tennis"
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "Decemeber 19, 2019"
output: pdf_document
bibliography: bibliography.bib
---

@@

```{r, echo = FALSE}

@@

```{r, echo=FALSE, message=F, warning=F}
W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

```
Similarly, we want to consider the 2002 US Open for the men's semifinalists. Using the same method outline above, we can see in Figure 2 that we predict P. Sampras to win the tournement, and in fact he did win this tournament.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mOpen <- read_csv('2002 US Open- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

```
```{r, message=F, warning=F}
wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 3',
          subtitle = "2002 Women's Wimbledon")
```
```{r, message=F, warning=F}
mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

For our extension, we ran the same method on data from the 2019 Wimbledon Tournament for both men's and women's. The data for probability of winning a rally can be found in Table 4. As seen in Figure 5, we predict that B. Strycoa wins the tournament, but S. Halep actually won the 2019 Women's Wimbledon. Similarly, in Figure 6 we predict that Rodger Federer and Rafeal Nadal essentially have an equal probability of winning the tournement, but it was Novak Djokovic who actually won the tournement. Again, the discrepencies between who won the tourment and what we predicted are discussed in the limitations section.  
```{r, echo =FALSE, warning=FALSE}
#Women
wWim19 <- read_csv('2019 Womens Wimbledon.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

```{r, warning=FALSE, echo=FALSE, message=F}

>>>>

---
title: "Tennis"
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "Decemeber 19, 2019"
output: pdf_document
header - input: 
  - \usepackage{float}
bibliography: bibliography.bib

---

@@

```{r, echo = FALSE, fig.pos="H"}

@@

```{r, echo=FALSE, message=F, warning=F, fig.pos="H"}
W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

Similarly, we want to consider the 2002 US Open for the men's semifinalists. Using the same method outline above, we can see in Figure 2 that we predict P. Sampras to win the tournement, and in fact he did win this tournament.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
mOpen <- read_csv('2002 US Open- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

```
```{r, message=F, warning=F, fig.pos="H"}
wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 3',
          subtitle = "2002 Women's Wimbledon")
```
```{r, message=F, warning=F, fig.pos="H"}
mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

For our extension, we ran the same method on data from the 2019 Wimbledon Tournament for both men's and women's. The data for probability of winning a rally can be found in Table 4. As seen in Figure 5, we predict that B. Strycoa wins the tournament, but S. Halep actually won the 2019 Women's Wimbledon. Similarly, in Figure 6 we predict that Rodger Federer and Rafeal Nadal essentially have an equal probability of winning the tournement, but it was Novak Djokovic who actually won the tournement. Again, the discrepencies between who won the tourment and what we predicted are discussed in the limitations section.  
```{r, echo =FALSE, warning=FALSE, fig.pos="H", message=FALSE}
#Women
wWim19 <- read_csv('2019 Womens Wimbledon.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}
